Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-04-05 analyses/reproduce_analyses.Rmd

# Revised food-web model after removing non-significant terms
foodweb_model <- glmer(
  gall_survival ~ 
    Foodweb + 
    (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:sc.log.Clutch.1 +
    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:sc.sqrt.Pref.2 +
    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
summary(foodweb_model)
```

>>>>

# Revised food-web model after removing non-significant terms
foodweb_model <- glmer(
  gall_survival ~ 
    Foodweb + 
    (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
    Foodweb:sc.log.Clutch.1 +
    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
    Foodweb:sc.sqrt.Pref.2 +
    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
    (1|Genotype/Plant_Position/Gall_Number),
  data = gall_selection.df,
  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
summary(foodweb_model)
car::vif(foodweb_model) # higher VIF than I anticipated
car::vif(foodweb_model) 
```
